%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Forward Deployed Engineer | Software Engineer} % Job title
{Palantir} % Organization
{London, United Kingdom} % Location
{Apr. 2020 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Started and converted a pilot with a large client in one of the largest growing industries at Palantir}
\item {As technical lead I oversaw the technical strategy of our engagement and managed a small team of engineers}
\item {Implemented several tools used by the client for foundational workflows}
\item {As a backend engineer I worked on the core compute foundations of Foundry and implemented a new user facing feature}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Backend Software Engineer and Product Manager} % Job title
{N26} % Organization
{Berlin, Germany} % Location
{Jun. 2018 - Feb. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Planned sprints, coordinated and implemented the launch of new card colours, and became primary point of contact for our card issuing provider}
\item {Helped in the design, planning, implementation, and migration of the microservice responsible for card lifecycle management}
\item {Ran sprints, plannings, reviews, and retros as PO of the Bank Core team responsible for core payment services including SEPA}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Autonomos} % Organization
{Berlin, Germany} % Location
{May. 2017 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked as part of a team implementing a full stack autonomous driving solution}
\item {Researched the feasibility of integrating certain computer vision algorithms into the perception pipeline}
\item {Wrote a proof of concept for processing and extracting obstacles from stereo data}
\end{cvitems}
}

%------------------------------------------------    

% \cventry
% {Tutor} % Job title
% {Key Admissions} % Organization
% {Vancouver, Canada} % Location
% {Jan. 2017 - Apr. 2017} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {Taught students from 2nd grade all the way to 12th grade in Maths, Physics, and Chemistry, both IB and BC curriculum}
% \end{cvitems}
% }

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Axiom Zen / Routific} % Organization
{Vancouver Canada} % Location
{Jan. 2014 - Apr. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Did front end design for website application using industry standard technologies (MEAN stack)}
\item {Created automation tools (in Python) for setting up email templates and estimating traffic time which sped up map making}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Software Engineer and Product Manager} % Job title
{TomTom} % Organization
{Amsterdam, Netherlands} % Location
{May. 2013 - Sept. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented clustering algortihm (k-means) to find common destinations}
\item {Created a design proposal for wearable fitness tracker}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}